Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex

  \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image01.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image02.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image03.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image04.png}
  \includegraphics[height = 0.2\textwidth,trim={3.5cm 0cm 0cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image05.png}
  \caption{\label{fig:extensionalNonsymmetric}Dynamics of a vesicle pair
  in a planar extensional flow. ${\cal H} = 0.7$ for the first three
  rows, and ${\cal H}=0.6$ for the bottom row. From top to bottom, the
  initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1. The
  reduced area is $\Delta A = 0.75$, the extension rate $\dot\epsilon= 0.09$
%  \todo[inline]{Yuan: Can you look and see what extension rates you
%  did for the runs that do not indicate the rate in the file name?} 
  and the adhesion distance $\delta = 0.4$. }
  \end{figure}

@@

\begin{figure}[htp]
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image01.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image02.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image03.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image04.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image05.png}
    \\
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image01.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image02.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image03.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image04.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image05.png}
    \\
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image01.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image02.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image03.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image04.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image05.png}
  \caption{\label{fig:extensional1} A vesicle doublet in an extensional
  flow with an initial inclination angle $\theta=\pi$.  The reduced
  area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
  the separation distance is $\delta = 0.4$, and the extension rate is
  $\dot\epsilon = 0.02$ ({\em top}), $\dot\epsilon=0.07$ ({\em middle}), and $\dot\epsilon =
  0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
  square, is the stagnation point.}
  \end{figure}

@@

 \begin{figure}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image01.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image02.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image03.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image04.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image05.png}
  \caption{\label{fig:extensional3} A vesicle doublet in an extensional
  flow with an initial inclination angle $\theta=\pi$.  The reduced area
  is $\Delta A = 0.8$, the Hamaker constant $\mathcal{H} = 0.7$, the
  separation distance is $\delta = 0.4$, and the extension rate $\dot\epsilon
  = 0.1$.  The center of the vesicle, denoted with a black square, is a
  stagnation point.}
\end{figure}

@@

\begin{figure}[htp]
  \begin{tabular}{@{}p{0.3\linewidth}@{\quad}p{0.3\linewidth}@{\quad}p{0.3\linewidth}@{}}
  \subfigimg[width=\linewidth]{(a)}{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf} &
  \subfigimg[width=\linewidth]{(b)}{figs/adR4em1adS7em1_finalInclinationAngle.pdf} &
  \subfigimg[width=\linewidth]{(c)}{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \end{tabular}
%  \includegraphics[height=0.26\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
%  \includegraphics[height=0.26\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
%  \includegraphics[height=0.26\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \caption{\label{fig:extensionalInclinationAngle} (a) The inclination
  angle of a doublet formed by vesicles of reduced area $\Delta A = 0.7$
  in an extensional flow with an extension rate $\dot\epsilon$.  (b) The final
  inclination angle of doublets.  At larger extension rates, the
  doublet is broken by the flow.  (c) A phase diagram of the long-time
  behavior of a fluid trap formed by two adhering vesicles in an
  extensional flow.  Results are not reported for some of the low
  extension rates since the doublet had not tilted to an equilibrium
  inclination angle for the given time horizon.}
\end{figure}

>>>>

  \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image01.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image02.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image03.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image04.png}
  \includegraphics[height = 0.2\textwidth,trim={3.5cm 0cm 0cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image05.png}
  \caption{\label{fig:extensionalNonsymmetric}Dynamics of a vesicle pair
  in a planar extensional flow. ${\cal H} = 0.7$ for the first three
  rows, and ${\cal H}=0.6$ for the bottom row. From top to bottom, the
  initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1. The
  reduced area is $\Delta A = 0.75$, the extension rate $\dot\epsilon=
  0.09$ and the adhesion distance $\delta = 0.4$.  The color coding is
  the tension.}
  \end{figure}

@@

\begin{figure}[htp]
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image01.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image02.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image03.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image04.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image05.png}
    \\
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image01.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image02.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image03.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image04.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image05.png}
    \\
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image01.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image02.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image03.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image04.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image05.png}
  \caption{\label{fig:extensional1} A vesicle doublet in an extensional
  flow with an initial inclination angle $\theta=\pi$.  The reduced
  area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
  the separation distance is $\delta = 0.4$, and the extension rate is
  $\dot\epsilon = 0.02$ ({\em top}), $\dot\epsilon=0.07$ ({\em middle}), and $\dot\epsilon =
  0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
  square, is the stagnation point.  The color coding is the tension.}
  \end{figure}

@@

 \begin{figure}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image01.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image02.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image03.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image04.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image05.png}
  \caption{\label{fig:extensional3} A vesicle doublet in an extensional
  flow with an initial inclination angle $\theta=\pi$.  The reduced area
  is $\Delta A = 0.8$, the Hamaker constant $\mathcal{H} = 0.7$, the
  separation distance is $\delta = 0.4$, and the extension rate
  $\dot\epsilon = 0.1$.  The center of the vesicle, denoted with a black
  square, is a stagnation point.  The color coding is the tension.}
\end{figure}

@@

\begin{figure}[htp]
  \begin{tabular}{@{}p{0.3\linewidth}@{\quad}p{0.3\linewidth}@{\quad}p{0.3\linewidth}@{}}
  \subfigimg[width=\linewidth]{(a)}{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf} &
  \subfigimg[width=\linewidth]{(b)}{figs/adR4em1adS7em1_finalInclinationAngle.pdf} &
  \subfigimg[width=\linewidth]{(c)}{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \end{tabular}
%  \includegraphics[height=0.26\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
%  \includegraphics[height=0.26\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
%  \includegraphics[height=0.26\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \caption{\label{fig:extensionalInclinationAngle} (a) The inclination
  angle of a doublet formed by vesicles of reduced area $\Delta A = 0.7$
  in an extensional flow with an extension rate $\dot\epsilon$.  For all
  extension rates, the vesicle's orientation angle tends to a value in
  $(\frac{\pi}{2},\pi)$. (b) The final inclination angle of the doublets
  for a variety of reduced areas.  At larger extension rates, the
    doublet is broken by the flow.  (c) A phase diagram of the long-time
    behavior of a fluid trap formed by two adhering vesicles in an
    extensional flow.  Reduced areas and extension rates that do not
    form a doublet are marked in red, and those that do form a doublet
    are marked in blue.  For the blue marks, the size is proportional to
    the final inclination angle.  Squares indicate that the doublet had
    not tilted to an equilibrium inclination angle in the given time
    horizon.}
\end{figure}
